### 2022-04-24 background.tex
Update metric description
Add waveform example

Assume there are $N$ speakers talking simultaneously, they are called $s_1, s_2, \dots s_N$. The waveform of speech utterance for each speaker is $U_i\left( t \right)$ while $i\in\left[ 1, N \right]$. Assume the noise is $e\left( t \right)$.
So the mixed utterance $X\left( t \right)$ is as equation~\ref{eq:mixed}.
\begin{equation}
    X\left( t \right) = \sum\limits_{i=1}^N U_i\left( t \right) + e\left( t \right)
    \label{eq:mixed}
\end{equation}
For the mission of Target Speaker Separation (TSS) Task. Assume we only need to extract the voice of speaker $s_n$ from $X\left( t \right)$ and we have the reference utterance from $s_n$, denoted as $R_n$.
The task is given $X\left( t \right) = \sum\limits_{i=1}^N U_i\left( t \right) + e\left( t \right)$ and $R_n$, we need to get $U_n\left( t \right)$.

@@

Using meaningful metrics to define the performance of the separation system is important.

>>>>

Assume there are $N$ speakers talking simultaneously, they are called $s_1, s_2, \dots s_N$. The waveform of speech utterance for each speaker is $U_i\left( t \right)$ while $i\in\left[ 1, N \right]$. Assume the noise is $e\left( t \right)$.
So the mixed utterance $X\left( t \right)$ is as equation~\ref{eq:mixed}.
\begin{equation}
    X\left( t \right) = \sum\limits_{i=1}^N U_i\left( t \right) + e\left( t \right)
    \label{eq:mixed}
\end{equation}
One waveform example is as figure~\ref{fig:waveform}.
\begin{figure}[!htbp]
    \centering
    \includegraphics[width=0.8\textwidth]{img/waveform}
    \caption{One example of how waveform looks like}
    \label{fig:waveform}
\end{figure}

For the mission of Target Speaker Separation (TSS) Task. Assume we only need to extract the voice of speaker $s_n$ from $X\left( t \right)$ and we have the reference utterance from $s_n$, denoted as $R_n$.
The task is given $X\left( t \right) = \sum\limits_{i=1}^N U_i\left( t \right) + e\left( t \right)$ and $R_n$, we need to get $U_n\left( t \right)$.

@@

Using meaningful metrics to define the performance of the separation system is important.
To evaluate the performance of separation system, the metric should be designed to objectively represent ``how good'' the extracted waveform is.
The idea of projecting one high dimensional vector onto another high dimensional vector comes in mind.
